\textbf{Designing a Security Management Layer for CDN Assets}

### 2016-02-19 tex/paper.tex
Added explaining figures for Mongo and project tree

@@

\subsubsection{Run-time of Operations}

@@

\par \textbf{Delete entity} \\
Deleting an entity is a constant time operation when that entity does not have any children. When
the entity has children all those children has to be deleted too which will be done in the same
manner as the project tree is built and therefore results in the same runtime, O(n) as an upper
bound, where n is the number of entities in the subtree.

>>>>

\subsubsubsection{GUID}
Global Unique Identifier - Usually in distributed environments normal incremented identifiers can
not be used as there can be insertions on several nodes at the same time. A GUID is generated by a
function that makes it impossible or extremely unlikely that the same identifier will be generated
and used again.

@@

\subsubsection{Run-time Complexity of Operations}
\begin{figure}[H] 
    \centering{
         \begin{tikzpicture}[nodes={draw, circle, fill=blue!20}, <-]
             \node{R}
             child{node{C} child{node{C}} child{node{C} child{node{M}} child{node{M}}}}
             child{node{C}};
         \end{tikzpicture}
    }
    \caption{Project Tree\\R - RootContainer, C - Container, M - Content}
    \label{fig:project_tree}
\end{figure}

In the user interface the stored data is always represented and worked on as a tree, or a forest if
all projects are considered. For a very small project that tree could look like the example in
Figure~\ref{fig:project_tree}. This is however not what the actual storage of the data looks like.

\begin{figure}[H] 
    \centering
    \renewcommand{\arraystretch}{1.3}
    \begin{tabular}{|r|c|l|}
        \hline
        \textbf{Type} & \textbf{Id} & \textbf{Parent Id} \\
        \hline
        RootContainer & 1 & 1 \\
        Container     & 2 & 1 \\
        Container     & 3 & 1 \\
        Container     & 4 & 2 \\
        Container     & 5 & 2 \\
        Content       & 6 & 5 \\
        Content       & 7 & 5 \\
        \hline
    \end{tabular}
    \renewcommand{\arraystretch}{1.0}
    \caption{Simplified Representation of the Actual Storage}
    \label{fig:storage}
\end{figure}

The actual storage of the data is represented by documents in a flat document storage, which is in
this case MongoDB. A very simplified version of how the data is stored can be seen in
Figure~\ref{fig:storage}. One important point that differs in the example and in the actual storage
is that GUIDs are used for identifiers and not incremented numbers, as that would not work in
distributed environments.

As the data is not stored as a tree, but rather as separate documents loosely referring to each
other, the run-time complexity is not obvious and that is what is discussed in this section.\\

@@

\par \textbf{Delete entity} \\
Deleting an entity is a constant time operation when that entity does not have any children. When
the entity has children all those children has to be deleted too which will be done in the same
manner as the project tree is built and therefore results in the same runtime, O(n) as an upper
bound, where n is the number of entities in the subtree.\\
